---
title: "Let's Go To Court Episode Analysis"
author: "Courtney Russ"
date: "`r Sys.Date()`"

output:
  rmdformats::material:
    code_folding: show
    thumbnails: false
    fig_width: 6
    fig_height: 4
    df_print: kable
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Data

## This is an analysis of Let's Go To Court episodes based on [this spreadsheet](https://docs.google.com/spreadsheets/u/0/d/1fjcQMWOd-nlz3OUZ3f3MdCYAkJXJWN-2fsVSDu0bB_U/htmlview#). <br>

This information is incomplete; this file will be periodically updated as more information is added.
<br><br>
The spreadsheet was started by stephhayes and bizzybee429 on the Let's Go To Court Patreon discord server and has been contributed to by many other members.  <br><br>

### [My Full Portfolio](https://www.datascienceportfol.io/CourtneyRuss)

# Setup
## Load Packages

```{r packages, message=FALSE}
library(googlesheets4)
library(skimr)
library(tidyverse)
library(knitr)
library(textTinyR)
library(textstem)
library(tidytext)
library(tm)
library(wordcloud)
library(stringr)
library(patchwork)
```

## Load data
The [googlesheets4](https://googlesheets4.tidyverse.org) package is used to load the data via the Sheet API V4. 

```{r data, message=FALSE}
sheet_key <- "1fjcQMWOd-nlz3OUZ3f3MdCYAkJXJWN-2fsVSDu0bB_U" 
# sheet_key is a static reference to the sheet

sheet <- gs4_get(sheet_key)

# Get Sheet 1 - regular episodes
datareg <- read_sheet(sheet, sheet = 1) %>%
  mutate(type = 'Regular') 

# Get Sheet 2 - bonus episodes
databonus <- read_sheet(sheet, sheet = 2) %>%
  mutate(type = 'Bonus') %>%
  rename(`...1` = `Episode Number`,
         `...5` = `Brandi's Case`) # renaming for consistency to allow merge of datasets

# Combine into one dataset - 'stacks' both on top of each other
data <- bind_rows(datareg, databonus) 
```

## Clean Data
During cleaning I have

- removed columns that I'm not using

- renamed the columns for easier reference

- made the episode number numeric

- removed episodes with empty titles - the spreadsheet is pre-numbered for future episodes so these extra rows need to be removed.

```{r clean}
data_clean <- data %>%
  select(-`Inside Joke Origin`, 
         -`Discord Questions Answered`, 
         -`Interesting Facts/Anecdotes`, 
         -`Release Date`) %>%
  rename(episode_num = `...1`,
         title = `Episode Title`,
         summary = `Episode summary/Show notes`,
         b_case = `...5`,
         b_disc = `Brandi's Disclaimers`,
         k_case = `Kristin's Case`,
         k_disc = `Kristin's Disclaimers`,
         after_dark = `After Dark?`,
         fun_facts = `Tim Pound's Fun Facts`,
         not_fun_facts = `Kristin's Not-So-Fun Fun Facts`,
         guests = Guests,
         guest_case = `Guest's Case`,
         songs = `Songs Sung`,
         k_source = `Kristin's Sources`,
         b_source = `Brandi's Sources`,
         g_source = `Guest's Sources`) %>%
  mutate(episode_num = as.numeric(sub("#", "", episode_num))) %>%
  filter(!is.na(title))
```

## Quick Look at Cleaned Data

```{r skim}
skim(data_clean)
```

# Disclaimers

## Filter Disclaimers 

Here I'm filtering for just the two disclaimer columns then pivoting them into a tidy data format and removing blanks. There is some inconsistency in capitalisation in the 'disclaimer' column so I've also standardised this. 

```{r disclaimers}
b_disclaimers <- data_clean %>%
  select(episode_num, title, b_case, b_disc, type) %>%
  rename(disclaimer = b_disc,
         case = b_case) %>%
  mutate(name = 'Brandi') %>%
  filter(!is.na(disclaimer))

k_disclaimers <- data_clean %>%
  select(episode_num, title, k_case, k_disc, type) %>%
  rename(disclaimer = k_disc,
         case = k_case) %>%
  mutate(name = "Kristin") %>%
  filter(!is.na(disclaimer))

disclaimers <- bind_rows(b_disclaimers, k_disclaimers) %>%
  separate_rows(disclaimer, sep = " and ") %>%
  arrange(episode_num) %>%
  mutate(disclaimer = case_when(
    disclaimer == 'old Timey Disclaimer' ~ 'Old Timey Disclaimer',
    disclaimer == 'Old timey case, but no proper disclaimer' ~ 'Old Timey Disclaimer',
    disclaimer == 'International Case Disclaimer' ~ 'International Disclaimer',
    TRUE ~ disclaimer
  ))
```

## View Disclaimers
```{r view disclaimers}
kable(disclaimers, col.names = c("Ep Number", "Title", "Case", "Disclaimers", "Episode Type", "Name"))

```

## Summarise 
Summarising the data for plotting.

```{r summarise}
summary_disc <- disclaimers %>%
  count(name, disclaimer) %>%
  rename(count = n) 
```

## Plot

```{r plot disclaimers, fig.fullwidth=TRUE}
# Set custom colours
colours <- RColorBrewer::brewer.pal(5, "Accent")
disc_colours <- c(colours[1], colours[5])


# Plot
ggplot(summary_disc, aes(x = disclaimer, y = count, fill = name)) +
  geom_bar(stat = "identity") +
  scale_fill_manual(values = disc_colours) +
  labs(title = "Disclaimer Counts by Host",
       y = "Count",
       fill = "Name") +
  theme_minimal() + 
  theme(legend.position = "right", 
        legend.title = element_blank(), 
        axis.text.x = element_text(angle = 45, hjust = 1), 
        axis.title.x = element_blank(),
        axis.title.y = element_blank())
```
<br>
Kristin uses a lot more disclaimers than Brandi, especially the Old Timey Disclaimer. 

# Top Words in Summary

These are the words that are most used in the 'summary' column.

## Process data

```{r text, warning=FALSE, message=FALSE}
remove <- "WARNING: The audio in this episode is rough\\. What can we say\\? We were young\\(ish\\), dumb, and thought we’d save a little money by sharing one microphone\\. Yeah\\. The audio quality improves drastically after episode 9\\."

word_df <- data_clean %>%
  mutate(
    summary = str_replace_all(summary, remove, ""),
    summary = str_replace_all(summary, "(?<!\\d)-(?!\\d)", " ") %>%
    str_replace_all("[^A-Za-z\\s]", "")
  ) %>%
  unnest_tokens(word, summary) %>%
  mutate(word = lemmatize_words(word)) %>%
  anti_join(stop_words) %>%
  filter(!is.na(word)) %>%
  filter(!word %in% c("kristin", "brandi"))

word_counts <- word_df %>%
  group_by(word) %>%
  summarise(count = n()) %>%
  arrange(desc(count))

top_words <- word_counts %>%
  top_n(n=20, wt=count)
```

## Plot

```{r plot words}
ggplot(top_words, aes(x = count, y = fct_reorder(word, count))) +
  geom_bar(stat = "identity", fill = disc_colours[1], alpha = 0.8) +
  labs(title = "Top Words Used in Episode Summary", x = "Count", y = "") +
  theme_minimal() +
  theme(axis.title.y = element_blank())
```

## Word Cloud

```{r wordcloud, warning=FALSE, message=FALSE}
wordcloud(
  words = word_df$word,
  scale = c(3, 0.5),
  min.freq = 15, 
  random.order = FALSE, 
  colors = brewer.pal(8, "Dark2")
)
```

# Guests
## Prepare Data
Here I'm selecting for episodes with a value for 'guests' then standardising the value for each person's name. Non-name information from the 'guests' column is moved into the 'Notes' column.

```{r guests}

guests <- data_clean %>%
  select(type, episode_num, title, guests, guest_case) %>%
  filter(!is.na(guests)) %>%
  mutate(guest = case_when(
    grepl("norm|norman", guests, ignore.case = TRUE) ~ "Norman",
    grepl("dp|daryl", guests, ignore.case = TRUE) ~ "DP",
    TRUE ~ guests
  )) %>%
  mutate(Notes = str_replace_all(guests, c("Norman" = "", "Norm" = "", "Caruso" = "", "DP" = "", "Daryl" = ""))) %>%
  select(-guests) %>%
  mutate(Notes = str_trim(str_replace(Notes, "^[[:punct:][:space:]]+", "")),
         guest_case = coalesce(guest_case, "None")) %>%
  select(type, episode_num, title, guest, guest_case, Notes) %>%
  arrange(type, episode_num) 
```


## View Guest Table
```{r guests view}

kable(guests, col.names = c("Episode Type", "Episode Num", "Title", "Guest", "Case", "Notes"))

```

## Summarise for Plot
```{r guest summary}
guest_summary <- guests %>%
  group_by(guest) %>%
  summarise(count = n())
```

## Plot

```{r guest plot}
ggplot(guest_summary, aes(x = guest, y = count, fill = guest)) +
  geom_bar(stat = "identity") +
  labs(title="Visitor Counts",
       y="Count") +
  theme_minimal() + 
  theme(axis.title.x = element_blank(),
        legend.position = "none")

```
<br>

DP needs to make a few more appearances to catch up! 

# Songs

## Data Preparation
I've filtered the data for episodes where there is a value for 'songs' and summarised it by episode type (regular or bonus).
```{r songs}
songs <- data_clean %>%
  select(type, episode_num, title, songs) %>%
  filter(!is.na(songs))

song_type <- songs %>%
  group_by(type) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

```

## Plot
```{r plot songs}
g1 <- ggplot(song_type, aes(x = "", y = count, fill = type)) +
  geom_bar(width = 1, stat = "identity") +
  geom_text(aes(label = paste0(round(percentage), "%")), 
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  theme_minimal() +
  theme(axis.line = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        panel.grid = element_blank(),
        plot.margin = unit(rep(0, 4), "cm"),
        plot.background = element_blank()) +  # Remove plot background
  labs(title = "Episodes with Songs",
       fill = "Episode Type",
       y = "Count") +
  theme_void() +
  scale_fill_manual(values = disc_colours)

# Compare to overall episodes
overall_count <- data_clean %>%
  group_by(type) %>%
  summarise(count = n()) %>%
  mutate(percentage = count / sum(count) * 100)

g2 <- ggplot(overall_count, aes(x = "", y = count, fill = type)) +
  geom_bar(width = 1, stat = "identity") +
  geom_text(aes(label = paste0(round(percentage), "%")), 
            position = position_stack(vjust = 0.5)) +
  coord_polar(theta = "y") +
  theme_minimal() +
  theme(axis.line = element_blank(),    # Remove the axis line
        axis.text = element_blank(),    # Remove axis text
        axis.ticks = element_blank(),   # Remove axis ticks
        panel.grid = element_blank(),   # Remove grid lines
        plot.margin = unit(rep(0, 4), "cm"),
        plot.background = element_blank()) +  # Remove plot background
  labs(title = "Episodes Overall",
       fill = "Episode Type",
       y = "Count") +
  theme_void() +
  scale_fill_manual(values = disc_colours)

(g1 | g2) + plot_layout(guides = "collect")



``` 
<br>
Bonus episodes make up just 15% of all episodes but account for 31% of episodes with songs sung.

# Tim Pound's Fun Facts
## Get out your Fun Fact Journal

Brandi sometimes shares fun facts about her dad. If you haven't kept track of them in your own Fun Fact Journal, they're summarised for you here.

```{r Tim Pound}
tim_pound <- data_clean %>%
  select(episode_num, title, fun_facts) %>%
  filter(!is.na(fun_facts)) %>%
  arrange(episode_num)

kable(tim_pound, col.names = c("Episode Num", "Episde", "Tim Pound's Fun Facts"))
```

# Kristin's Not-So-Fun Fun Facts
### Some of us have different definitions of 'fun'

```{r not fun facts}
not_fun_facts <- data_clean %>%
  select(episode_num, title, not_fun_facts) %>%
  filter(!is.na(not_fun_facts)) %>%
  arrange(episode_num)

kable(not_fun_facts, col.names = c("Episode Num", "Episode", "Kristin's Not-So-Fun Fun Facts"))

```

